---
title: "NL_Modeling"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(zeallot)
library(boot)
setwd("~/Research/Pioneer/Project/Predicting-Poverty/scripts/")
```

# Analysis of Night Light Data and Poverty

Loading main dataframe:
```{r}
df <- read.csv("../processed/nl_wealth_data.csv")
```

### Simple Linear Model of all variables
```{r}
lm <- lm(wealth~mean + median + std + max + min, data=df)
plot(lm)
summary(lm)
```

Observe that the quantile plot shows severe deviation from normality and outliers. This can be potentially resolved with bootstrapping. Further, I beleive that most of the outliers correspond to cities and therefore have a much larger amount of nightlight than surrounding regions but potentially not as much wealth.

Further, note that STD, MAX, MEDIAN are not significant at the $\alpha = 0.01$ level. We remove them from the model in later steps.

# Simple Linear Model of only mean, median, min

```{r}
lm <- lm(wealth~mean + median + min, data=df)
plot(lm)
summary(lm)
```

This model seems to have a very high $r_{\text{adj}}^2$ value. However, it still shows deviations from normality and outliers.

# Simple Linear Model of only mean

```{r}
lm <- lm(wealth~mean, data=df)
plot(wealth~mean, data=df)
abline(lm)
plot(lm)
summary(lm)
```
Here is just a plot of mean. Also, you have a chance to actually see the data and the strong correlation.

# Bootstrapped Linear Model only mean

```{r}
set.seed(42)
N <- 5000
boot_func <- function(d, i) {
    return(summary(lm(wealth~mean, data=d[i,]))$coeff[2])
}
boot_res <- boot(df, boot_func, R = N)
hist(boot_res$t, xlab="Slopes")

boot.ci(boot_res)
```

Bootstrapping gives the confidence interval for the slope. I need to investigate it more thoroughly.